{Gravitational wave sources in our Galactic backyard:}\\{Predictions for BHBH, BHNS and NSNS binaries detectable with LISA

### 2022-01-22 paper/tex/sections/results.tex
missing bracket

BHBHs with unequal masses typically come from progenitors that also had more extreme mass ratios at birth ($90$ and $30\unit{M_{\odot}}$ are typical for the progenitors of detectable BHBH systems in our simulations. The primary in such systems experiences strong mass loss by winds before filling its Roche lobe. This mostly happens during its early hydrogen-shell burning phase. The wind mainly reduces the mass of the envelope, but does not have a very strong effect on the core. By the time the primary fills its Roche lobe, it has become less massive and the mass ratio is closer to one. This favours stable mass transfer. The massive core of the primary star typically becomes the more massive BH. Accretion on the secondary star is limited and the secondary eventually provides the less massive black hole.

>>>>

BHBHs with unequal masses typically come from progenitors that also had more extreme mass ratios at birth ($90$ and $30\unit{M_{\odot}}$ are typical for the progenitors of detectable BHBH systems in our simulations). The primary in such systems experiences strong mass loss by winds before filling its Roche lobe. This mostly happens during its early hydrogen-shell burning phase. The wind mainly reduces the mass of the envelope, but does not have a very strong effect on the core. By the time the primary fills its Roche lobe, it has become less massive and the mass ratio is closer to one. This favours stable mass transfer. The massive core of the primary star typically becomes the more massive BH. Accretion on the secondary star is limited and the secondary eventually provides the less massive black hole.
